---
title: "Untitled"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
```



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(palmerpenguins)
library(easystats)
library(equatiomatic)
library(pander)
library(broom)
library(kableExtra)
install.packages("kableExtra")
```

## Hey look, it's penguins! 

```{r}

```

Here's a look at the palmer penguins dataset. 

```{r}
penguins %>% glimpse
```

The steps of data science are 
1. import 
2. clean 
3. visualize 
4. model 
5. report

We don't need to do any real cleaning for this data set. But we can show some pretty pictures.

```{r}
p <- penguins %>% 
  filter(!is.na(sex)) %>% 
  ggplot(aes(x=species, y=body_mass_g, color = sex)) + 
  geom_boxplot() + 
  geom_jitter(color = 'black', alpha = .25, width = .2) + 
  labs(x = "Species", y = "Body mass (g)", color = "Sex")
#plotly::ggplotly(p)
#javascript
```

Here we see that male and female penguins have distinct body mass distributions for each specis of penguin. Don't believe your eyes? 
Here are some stats: 

```{r}
mod <- penguins %>% 
  filter(!is.na(sex)) %>% 
  glm(data= ., 
      formula = body_mass_g ~sex * species)

```

```{r}
mod %>%
  tidy %>% 
  kable %>% 
  kable_classic(lightable_options = "hover")

#kableExtra is really really good for table design (specifically html output)
```


The equation for our model is: 
```{r}
equatiomatic::extract_eq(mod)
```

#rmdformats